---
title: "Plate Reader"

---

Install the library
```{r}
#install.packages("readxl")
#install.packages("dplyr", dep = TRUE)
#install.packages("stat_smooth")
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)
library(outliers)
library(gtools)

```

Read the data - make sure you delete the second row with temp - then you do not need to specify what type of the column you have
```{r}
#data <- read_excel("DO-PEPCPG_4Cand30C.xlsx", col_types = c("text", "text", "numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric"))
data <- read_excel("DO-PEPCPG_4Cand30C.xlsx")

names(data) <- gsub(" ", "_", names(data))
data
```
We dont need the first row - delete
```{r}
#data <- data[-1,]
#cols = c( 3, 4, 5,6,7,8,9,10) 
#data[,cols] = apply(data[,cols], 2, function(x) as.numeric(as.character(x)))
#data
```


sort the data base on Well_position
```{r}
data <- data[mixedorder(as.character(data$Well_positions)), ]
data
```


subtraction of the blank data
```{r}
data_diff <-  data %>%
  group_by(grp = (row_number() - 1) %/% 2) %>%
  summarise_all(funs(ifelse(is.numeric(.), first(.) - last(.), first(.)))) %>%
  ungroup() %>%
  select(-grp)
data_diff <- select(data_diff, - Well_positions)
data_diff
```
Grubbs test
https://stackoverflow.com/questions/22837099/how-to-repeat-the-grubbs-test-and-flag-the-outliers
```{r}
grubbs.flag <- function(vector) {
  outliers <- NULL
  test <- vector
  grubbs.result <- grubbs.test(test)
  pv <- grubbs.result$p.value
  # throw an error if there are too few values for the Grubb's test
  if (length(test) < 3 ) stop("Grubb's test requires > 2 input values")
  na.vect <- test
  while(pv < 0.05) {
    outliers <- c(outliers,as.numeric(strsplit(grubbs.result$alternative," ")[[1]][3]))
    test <- vector[!vector %in% outliers]
    # stop if all but two values are flagged as outliers
    if (length(test) < 3 ) {
      warning("All but two values flagged as outliers")
      break
    }
    grubbs.result <- grubbs.test(test)
    pv <- grubbs.result$p.value
    idx.outlier <- which(vector %in% outliers)
    na.vect <- replace(vector, idx.outlier, NA)
    
  }
  return(na.vect)
}
num <- ncol(data_diff)
frag<- data_diff[,2:num]
frag<- as.data.frame(frag)
data_diff2<- as.data.frame(apply(frag,2,grubbs.flag))

#calculate how  many NA
na_count <-sapply(data_diff2, function(y) sum(length(which(is.na(y)))))
data.frame(na_count)

data_diff2$Layout <- data_diff$Layout
data_diff_gibbs <- data_diff2[complete.cases(data_diff2), ]
data_diff_gibbs
```



Calculate the mean and sd
```{r}

data_stat <- data_diff_gibbs %>% 
            group_by(Layout) %>%
            summarise_each(funs(mean(.), sd(.))) %>% ungroup()
data_stat
```
Take only mean data + first calculation 
```{r}
data_mean <- data_stat %>% select(Layout, ends_with("_mean"))

data_mean <- data_mean %>% 
  group_by(Layout) %>% 
  mutate(Q18=FL_18_mean/.$FL_18_mean[.$Layout == "ST1_1"]*.$Abs_18_mean[.$Layout == "ST1_1"]/Abs_18_mean,
         Q20=FL_20_mean/.$FL_20_mean[.$Layout == "ST1_1"]*.$Abs_20_mean[.$Layout == "ST1_1"]/Abs_20_mean,
         Q23=FL_23_mean/.$FL_23_mean[.$Layout == "ST1_1"]*.$Abs_23_mean[.$Layout == "ST1_1"]/Abs_23_mean,
         Q25=FL_25_mean/.$FL_25_mean[.$Layout == "ST1_1"]*.$Abs_25_mean[.$Layout == "ST1_1"]/Abs_25_mean,
         Q30=FL_30_mean/.$FL_30_mean[.$Layout == "ST1_1"]*.$Abs_30_mean[.$Layout == "ST1_1"]/Abs_30_mean,
         Q37=FL_37_mean/.$FL_37_mean[.$Layout == "ST1_1"]*.$Abs_37_mean[.$Layout == "ST1_1"]/Abs_37_mean,
         Q42=FL_42_mean/.$FL_42_mean[.$Layout == "ST1_1"]*.$Abs_42_mean[.$Layout == "ST1_1"]/Abs_42_mean
         
         )

data_mean
```


QY and viscosity calculated

```{r}
q <- data_mean %>% select(Layout, starts_with("Q"))
c <- (1.3325^2)/(1.4385^2)
t18 <- 18
t20 <- 20
t23<- 23
t25 <- 25
t30 <- 30
t37 <- 37
t42<- 42

QY_t <- q %>% 
  mutate(QY_T18= 0.0002*(2649.0219*t18^(-1.5448))^0.6019 ,
         QY_T20=0.0002*(2649.0219*t20^(-1.5448))^0.6019,
         QY_T23=0.0002*(2649.0219*t23^(-1.5448))^0.6019,
         QY_T25=0.0002*(2649.0219*t25^(-1.5448))^0.6019,
         QY_T30=0.0002*(2649.0219*t30^(-1.5448))^0.6019,
         QY_T37=0.0002*(2649.0219*t37^(-1.5448))^0.6019,
         QY_T42=0.0002*(2649.0219*t42^(-1.5448))^0.6019
         
         )

vis <- QY_t %>% 
  group_by(Layout) %>% 
  mutate(vis18=((Q18*QY_T18*c)/0.0002)^(1/0.6019),
         vis20=((Q20*QY_T20*c)/0.0002)^(1/0.6019),
         vis23=((Q23*QY_T23*c)/0.0002)^(1/0.6019),
         vis25=((Q25*QY_T25*c)/0.0002)^(1/0.6019),
         vis30=((Q30*QY_T30*c)/0.0002)^(1/0.6019),
         vis37=((Q37*QY_T37*c)/0.0002)^(1/0.6019),
         vis42=((Q42*QY_T42*c)/0.0002)^(1/0.6019)
         
         ) %>% ungroup()
vis
```
Calculate an error
```{r}
errors<- merge(vis, data_stat)

errors <- errors %>%
  group_by(Layout) %>%
  mutate(e18 = sqrt((.$FL_18_sd[.$Layout == "ST1_1"]/.$FL_18_mean[.$Layout == "ST1_1"])^2+(.$Abs_18_sd[.$Layout == "ST1_1"]/.$Abs_18_mean[.$Layout == "ST1_1"])^2+(FL_18_sd/FL_18_mean)^2+(Abs_18_sd/Abs_18_mean)^2)*vis18,
         e20 = sqrt((.$FL_20_sd[.$Layout == "ST1_1"]/.$FL_20_mean[.$Layout == "ST1_1"])^2+(.$Abs_20_sd[.$Layout == "ST1_1"]/.$Abs_20_mean[.$Layout == "ST1_1"])^2+(FL_20_sd/FL_20_mean)^2+(Abs_20_sd/Abs_20_mean)^2)*vis20,
         e23 = sqrt((.$FL_23_sd[.$Layout == "ST1_1"]/.$FL_23_mean[.$Layout == "ST1_1"])^2+(.$Abs_23_sd[.$Layout == "ST1_1"]/.$Abs_23_mean[.$Layout == "ST1_1"])^2+(FL_23_sd/FL_23_mean)^2+(Abs_23_sd/Abs_23_mean)^2)*vis23,
         e25 = sqrt((.$FL_25_sd[.$Layout == "ST1_1"]/.$FL_25_mean[.$Layout == "ST1_1"])^2+(.$Abs_25_sd[.$Layout == "ST1_1"]/.$Abs_25_mean[.$Layout == "ST1_1"])^2+(FL_25_sd/FL_25_mean)^2+(Abs_25_sd/Abs_25_mean)^2)*vis25,
         e30 = sqrt((.$FL_30_sd[.$Layout == "ST1_1"]/.$FL_30_mean[.$Layout == "ST1_1"])^2+(.$Abs_30_sd[.$Layout == "ST1_1"]/.$Abs_30_mean[.$Layout == "ST1_1"])^2+(FL_30_sd/FL_30_mean)^2+(Abs_30_sd/Abs_30_mean)^2)*vis30,
         e37 = sqrt((.$FL_37_sd[.$Layout == "ST1_1"]/.$FL_37_mean[.$Layout == "ST1_1"])^2+(.$Abs_37_sd[.$Layout == "ST1_1"]/.$Abs_37_mean[.$Layout == "ST1_1"])^2+(FL_37_sd/FL_37_mean)^2+(Abs_37_sd/Abs_37_mean)^2)*vis37,
         e42 = sqrt((.$FL_42_sd[.$Layout == "ST1_1"]/.$FL_42_mean[.$Layout == "ST1_1"])^2+(.$Abs_42_sd[.$Layout == "ST1_1"]/.$Abs_42_mean[.$Layout == "ST1_1"])^2+(FL_42_sd/FL_42_mean)^2+(Abs_42_sd/Abs_42_mean)^2)*vis42
         
         )


final <- errors %>% select("Layout", starts_with("vis"), starts_with("e"))
final <- final %>% filter(!Layout == "ST1_1")
final
```
Function to get the correlation equation
https://gist.github.com/kdauria/524eade46135f6348140
```{r}
stat_smooth_func <- function(mapping = NULL, data = NULL,
                        geom = "smooth", position = "identity",
                        ...,
                        method = "auto",
                        formula = y ~ x,
                        se = TRUE,
                        n = 80,
                        span = 0.75,
                        fullrange = FALSE,
                        level = 0.95,
                        method.args = list(),
                        na.rm = FALSE,
                        show.legend = NA,
                        inherit.aes = TRUE,
                        xpos = NULL,
                        ypos = NULL) {
  layer(
    data = data,
    mapping = mapping,
    stat = StatSmoothFunc,
    geom = geom,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      method = method,
      formula = formula,
      se = se,
      n = n,
      fullrange = fullrange,
      level = level,
      na.rm = na.rm,
      method.args = method.args,
      span = span,
      xpos = xpos,
      ypos = ypos,
      ...
    )
  )
}


StatSmoothFunc <- ggproto("StatSmooth", Stat,
                      
                      setup_params = function(data, params) {
                        # Figure out what type of smoothing to do: loess for small datasets,
                        # gam with a cubic regression basis for large data
                        # This is based on the size of the _largest_ group.
                        if (identical(params$method, "auto")) {
                          max_group <- max(table(data$group))
                          
                          if (max_group < 1000) {
                            params$method <- "loess"
                          } else {
                            params$method <- "gam"
                            params$formula <- y ~ s(x, bs = "cs")
                          }
                        }
                        if (identical(params$method, "gam")) {
                          params$method <- mgcv::gam
                        }
                        
                        params
                      },
                      
                      compute_group = function(data, scales, method = "auto", formula = y~x,
                                               se = TRUE, n = 80, span = 0.75, fullrange = FALSE,
                                               xseq = NULL, level = 0.95, method.args = list(),
                                               na.rm = FALSE, xpos=NULL, ypos=NULL) {
                        if (length(unique(data$x)) < 2) {
                          # Not enough data to perform fit
                          return(data.frame())
                        }
                        
                        if (is.null(data$weight)) data$weight <- 1
                        
                        if (is.null(xseq)) {
                          if (is.integer(data$x)) {
                            if (fullrange) {
                              xseq <- scales$x$dimension()
                            } else {
                              xseq <- sort(unique(data$x))
                            }
                          } else {
                            if (fullrange) {
                              range <- scales$x$dimension()
                            } else {
                              range <- range(data$x, na.rm = TRUE)
                            }
                            xseq <- seq(range[1], range[2], length.out = n)
                          }
                        }
                        # Special case span because it's the most commonly used model argument
                        if (identical(method, "loess")) {
                          method.args$span <- span
                        }
                        
                        if (is.character(method)) method <- match.fun(method)
                        
                        base.args <- list(quote(formula), data = quote(data), weights = quote(weight))
                        model <- do.call(method, c(base.args, method.args))
                        
                        m = model
                        eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                                         list(a = format(coef(m)[1], digits = 3), 
                                              b = format(coef(m)[2], digits = 3), 
                                              r2 = format(summary(m)$r.squared, digits = 3)))
                        func_string = as.character(as.expression(eq))
                        
                        if(is.null(xpos)) xpos = min(data$x)*0.9
                        if(is.null(ypos)) ypos = max(data$y)*0.9
                        data.frame(x=xpos, y=ypos, label=func_string)
                        
                      },
                      
                      required_aes = c("x", "y")
)


```


Make a plot
```{r}
final_gat <- final %>% gather(key, value, -Layout) %>%
  extract(key, c("rep", "temp"), "([a-z]+)([0-9]+)") %>%
  spread(rep, value)

final_gat$temp <- as.numeric(final_gat$temp) 

ggplot(final_gat, aes(x = temp, y = vis, group = Layout, col = Layout)) +
  geom_point() +
  geom_errorbar(aes(ymin=vis-e,ymax=vis+e),width=.2) +
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),
                labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  geom_point(aes(shape = Layout),size=2, fill="white") + 
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed", size = 0.2) +
  #stat_smooth(method=lm, se = FALSE, linetype = "dashed", size = 0.2) +
  stat_smooth_func(geom="text",method="lm",hjust=0,parse=TRUE)+
  theme_bw() +
  labs(x = "Temp in C", y = "Viscosity") +
  annotation_logticks(sides = "lr") 
```

http://ggplot.yhathq.com/docs/scale_y_log10.html

Kelvins
```{r}

final_gat_K <- final_gat %>% 
                mutate(Kel = (1000/(as.numeric(temp)+272.15)))

P <- ggplot(final_gat_K, aes(x = Kel, y = vis, group = Layout, col = Layout)) + 
   geom_errorbar(aes(ymin =vis - e, ymax = vis +e), width=.02)+
   #geom_line()+ 
   scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),
                labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  geom_point(aes(shape = Layout), size=3, fill="white") + 
  stat_smooth(method=lm, se = FALSE, linetype = "dashed", size = 0.2) +
  stat_smooth_func(geom="text",method="lm",hjust=0,parse=TRUE)+
  #geom_point(position=pd, size=3, shape=21, fill="white") + 
  #geom_point(aes(col = Layout)) +
  theme_bw() +
  #change names of axes!
  labs(x = "Temp in K", y = "Viscosity") +
  annotation_logticks(sides = "lr") 

P



```



Weird stuff Grzesiek wants..
```{r}

ea_cal<- as.data.frame(final_gat_K)
#mod <- lm(log10(vis) ~ Kel, data = ea_cal)

 #eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
  #                                       list(a = format(coef(mod)[1], digits = 3), 
  #                                            b = format(coef(mod)[2], digits = 3), 
  #                                            r2 = format(summary(mod)$r.squared, digits = 3)))

#eq
Ea <- ea_cal %>%
  group_by(Layout) %>%
  #do(data.frame(Coef = coef(lm(vis ~ temp, data=.))))
  do({
      mod = lm(log10(vis) ~ Kel, data = .)
      data.frame(Intercept = coef(mod)[1],
                 Slope = coef(mod)[2],
                R = summary(mod)$r.squared)
    }) %>%
  mutate(Ea = -(8.14 * Slope))
Ea
```